\chapter{UCNA Experiment}
\label{ch:UCNA_Experiment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The UCNA Experiment is a rather mature experiment, having taken data from
2007-2013, that aims to precisely determine a value of $A_{0}$, the neutron
$\beta$-decay asymmetry parameter. Here an overview of the experimental
apparatus and critical components is given, as well as previous measurements
of $A_{0}$ from other experiments. 


\section{Overview}
\label{sec:Overview}

Most neutrons utilized for experimental purposes possess energies upwards of
(insert number here) and are what we call fast neutrons. As (insert energy
spectrum figure for neutrons) figure blah shows, we define ultracold neutrons
as thos which have energies on the neV scale and typical speeds of ${<8m/s}$.
The goal of UCNA is to produce UCN in a solid deuterium source which is fed
higher energy neutrons via a spallation source at the end of an $800$ MeV
proton beam. These UCN are then guided towards a material trap where they can
decay. During travel, the UCN pass through a series of polarizing magnets
which allows the experimenter to control the spin state of the neutrons in
the trap during any run. Utilizing a strong ${~1 T}$ magnetic field in the
decay volume, decay electrons are guided towards detectors at either end of
the decay volume where their energy can be reconstructed. From knowledge about
the initial direction and the energy of the neutron, one can construct an
energy dependent asymmetry and determine a value for $A_{0}$.

\section{Los Alamos Neutron Science Center}
\subsection{800 MeV Proton Accelerator}

Blah Blah

\subsection{Ultracold Neutron Source}

Blah Blah

\subsection{Experimental Hall}

Here we highlight some of the other experiments taking place.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Setup}
\label{sec:Setup}

BLAH BLAH


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Previous measurements of $A_{0}$}
\label{sec:Previous_results}

\subsection{2010 UCNA Analysis}
\subsection{PERKEO}






