\chapter{Introduction}
\label{ch:Introduction}

The purpose of this dissertation is to describe in detail
the methods used in extracting the $\beta$-decay asymmetry parameter
for the UCNA Experiment. This chapter hopes to motivate the inception
of the parameter of interest and its role in the theory of $\beta$-decay.
Also introduced are characteristics of the neutron itself with an
emphasis on ultracold neutrons (UCN), the namesake of the UCNA experiment.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The Standard Model}
The Standard Model of particle physics encompasses everything we know about
interactions between particles and describes nature using the most fundamental
building blocks yet discovered. This section is used as an introduction
to these building blocks, the quarks and leptons, and to the mediators of the
interactions between them, to preface the upcoming descriptions of the neutron
and $\beta$-decay.

\subsection{The Building Blocks}

\subsection{The Forces}

\subsection{Symmetries}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Properties of the neutron}
\label{sec:neutronProperties}
Let us take a moment to give a very brief introduction to the neutron to motivate the
upcoming sections. This will also serve as a useful tool for those who are
unfamiliar with nuclear and field theories, as the following sections become
quite technical. The majority of this dissertation can be read and mostly understood
without much knowledge of the theoretical description behind neutron $\beta$-decay,
so the properties of the neutron are a natural starting point.

The neutron is a net neutrally charged composite particle. The terms net and
composite hint at the inner structure of the neutron, made up of fundamental
particles called quarks, in this case two down ($d$) quarks and one up ($u$) quark.
The quarks do carry charge, with the $u$ charge $+2/3$ and the $d$ charge
$-1/3$, so that the net charge of the neutron is zero. This can be compared
to the proton, another composite particle made up of three quarks (two $u$ and
one $d$ quark), whose net charge is $+1$ and the other nucleon found
within a nucleaus along with the neutron. Four other quarks exist,
the charm, strange, bottom, and top in order of increasing mass. The neutron
is the second lightest three-quark composite particle (baryon) 
behind only the proton.

The free neutron undergoes $\beta$-decay, defined as a transition from the neutron
to a proton, electron, and electron anti-neutrino,
\begin{equation*}
  n\rightarrow p + e^- + \bar{\nu}_{e}.
\end{equation*}
\noindent The three-body decay gives rise to a continuous energy spectrum
for the proton, electron, and anti-neutrino by conservation of energy and momentum
as seen in figure \ref{fig:spectralShapes}. The lifetime of the free neutron is
approximately fifteen minutes.


\section{$\beta$-decay of the neutron}

Prior to 1930, $\beta$-decay of nuclei was a polarizing topic of debate. Originally
only the decay electron was detected, and given such a two-body decay (the recoil
nucleus and the emitted electron being the two bodies) one would expect a discrete
electron energy defined by the difference in mass between mother and daughter
nuclei. Instead, a continuous energy spectrum was observed for the electron, which
initially led some to believe that energy conservation was moot. Pauli was not
convinced that energy conservation was violated and postulated that a neutral particle
was also emitted in the decay. This third particle would share the energy available
in the reaction, explain the continuous energy distribution of the electron, and go
on undetected as it would not interact electromagnetically. The particle was termed
the neutrino by Fermi, and it would be a crux of Fermi's theory of $\beta$-decay.
A quarter century later, the existence of the neutrino would be confirmed \cite{cowan1956detection}.

\subsection{Fermi's Theory of $\beta$-decay}
After Pauli postulated the existence of the neutrino to explain the continuous energy
distribution of the $\beta$-decay electron, Fermi attempted to theoretically describe
the process in a similar manner to the theory of emission of
gamma radiation from an excited nucleus \cite{fermi1934,wilson1968fermi}.
His theory relied on two postulates: the existence of the neutrino and that the nucleus consisted
of heavy particles only, the neutron and the proton. Both of these would turn out to be true.

\begin{table}[h]
  \caption{Transformation behavior of all possible bilinear covariants.} 
  \centering
  \begin{tabular}{l c }
    \hline \hline \\ [-1.75ex]
    $\bar{\psi}\psi$ & scalar \\ [0.50ex]
    $\bar{\psi}\gamma^5\psi$ & pseudoscalar \\ [0.50ex]
    $\bar{\psi}\gamma^{\mu}\psi$ & vector \\ [0.50ex]
    $\bar{\psi}\gamma^{\mu}\gamma^5\psi$ & axial vector \\ [0.50ex]
    $\bar{\psi}\sigma^{\mu\nu}\psi$ & antisymmetric tensor \\ [0.50ex]   
    \hline
  \end{tabular}
  \label{tab:bilinearCov}
\end{table}

Fermi's Hamiltonian took the form (written in a different manner from Fermi's original
paper on the subject for the sake of clarity) 
%
\begin{equation}
  H = C_V\big( \bar{\psi}_p \gamma_\mu \psi_n \big) \big( \bar{\psi}_e \gamma^\mu \psi_\nu \big), 
\end{equation}
%
where $\bar{\psi} \gamma_\mu \psi$ is a vector current when remembering how the
bilinear covariants transform under parity (see table \ref{tab:bilinearCov}). The assumption
that the current-current interaction would be of the vector-vector variety was a natural
choice as this is the case for electromagnetism.

Fermi's theory of $\beta$-decay treats the decay as a four-point contact interaction, where
the currents are evaluated at the same point in space and time \cite{renton1990}. The theory
worked well at predicting the energy spectrum of the electron from which
Fermi deduced that the neutrino must be nearly massless, but suffered one flaw. The vector
nature of the theory didn't allow for the observed allowed nuclear $\beta$-decay transitions
which transform the spin of the decaying nucleus. This was pointed out by Gamow and Teller in
1936 \cite{gamow1936}, where they show that a current-current interaction that transforms like
a pseudovector properly assigns the spins of the products in thorium decays. As such,
one can generalize Fermi's theory by including all possible bilinear covariant terms that
satisfy both Lorentz and translational invariance:
%
\begin{multline}
  H = C_S\big( \bar{\psi}_p \psi_n \big) \big( \bar{\psi}_e  \psi_\nu \big) 
  +C_V\big( \bar{\psi}_p \gamma_\mu \psi_n \big) \big( \bar{\psi}_e \gamma^\mu \psi_\nu \big) \\
  +C_T\big( \bar{\psi}_p \sigma^{\mu\nu} \psi_n \big) \big( \bar{\psi}_e \sigma^{\mu\nu} \psi_\nu \big) 
  +C_A\big( \bar{\psi}_p \gamma_\mu \gamma^5 \psi_n \big) \big( \bar{\psi}_e \gamma^\mu \gamma^5 \psi_\nu \big) 
  +C_P\big( \bar{\psi}_p  \gamma^5 \psi_n \big) \big( \bar{\psi}_e  \gamma^5 \psi_\nu \big),
\end{multline}
%
where the coefficients quantify the coupling to each respective current.

\subsubsection{Gamow-Teller vs. Fermi Transitions}

With the mention of the extension of Fermi's theory of $\beta$-decay by Gamow and Teller,
this is a natural place to introduce the 



\subsection{Parity Violation in Weak Decays}

\subsubsection{Lee and Yang}
Talk about the theta-tau conundrum.
Mention that inserting a pseudovector like term automatically violates parity
by mixing currents with opposite parity transformations thus causing the
Hamiltonian and the Parity operator to not commute.
%
\begin{multline}
  H =\big( \bar{\psi}_p \psi_n \big) \big(  C_S\bar{\psi}_e  \psi_\nu + C'_S\bar{\psi}_e \gamma^5 \psi_\nu \big) \\
  + \big( \bar{\psi}_p \gamma_\mu \psi_n \big) \big( C_V\bar{\psi}_e \gamma^\mu \psi_\nu + C'_V\bar{\psi}_e \gamma^\mu \gamma^5 \psi_\nu \big) 
  + \big( \bar{\psi}_p \sigma^{\mu\nu} \psi_n \big) \big( C_T\bar{\psi}_e \sigma^{\mu\nu} \psi_\nu + C'_T\bar{\psi}_e \sigma^{\mu\nu}\gamma^5 \psi_\nu \big) \\
  + \big( \bar{\psi}_p \gamma_\mu \gamma^5 \psi_n \big) \big( C_A\bar{\psi}_e \gamma^\mu \gamma^5 \psi_\nu + C'_A\bar{\psi}_e \gamma^\mu  \psi_\nu\big)
  + \big( \bar{\psi}_p  \gamma^5 \psi_n \big) \big( C_P\bar{\psi}_e  \gamma^5 \psi_\nu + C'_P\bar{\psi}_e \psi_\nu \big),
\end{multline}
%

Mention the experiments that can probe parity violation.
Talk about C. S. Wu experiment

\subsection{Correlation Coefficients}
Taking the interaction Hamiltonian from Lee and Yang with all generalized terms included,
Jackson, Treiman, and Wyld \cite{jackson1957a,jackson1957b} first derived an expression
for the differential decay rate for polarized nuclei as a function of the emitted electron momentum
and spin, the neutrino momentum, and the nuclear spin of the decaying nucleus.
Ebel and Feldman \cite{ebel1957} added terms to the expression of Jackson, Treiman, and Wyld,
and under the assumption that the spin of the mother nucleus and the spin of the outgoing electron
are observable this gives
%
\begin{multline}
  \frac{d\Gamma}{dE_e dE_\nu d\Omega_e d\Omega_\nu} = \frac{1}{2} \frac{F(\pm Z, E_e)}{\big( 2\pi \big)^5}
  p_e E_e \big( E^0 - E_e \big)^2 \\ \times \xi 
  \Bigg\{ 1 + a\frac{\boldsymbol{p_e \cdot p_\nu}}{E_e E_\nu} + b\frac{m_e}{E_e} 
  + \frac{\boldsymbol{\langle J \rangle}}{J} \Bigg[ A\frac{\boldsymbol{p_e}}{E_e}
    + B\frac{\boldsymbol{p_\nu}}{E_\nu} + D\frac{\boldsymbol{p_e \times p_\nu}}{E_e E_\nu}\Bigg] \\
  + \Bigg[ \frac{J(J+1)-3\langle (\boldsymbol{J \cdot \hat{\jmath}})^2 \rangle}{J(2J-1)} \Bigg]
  \Bigg( c\Bigg[ \frac{\boldsymbol{p_e} \times \boldsymbol{p_\nu}}{3E_eE_\nu} -
    \frac{(\boldsymbol{p_e\cdot \hat{\jmath}})(\boldsymbol{p_\nu\cdot \hat{\jmath}}) }{E_eE_\nu} \Bigg]
  + I \Bigg[ \frac{1}{3}\frac{\boldsymbol{\sigma \cdot p_\nu}}{E_\nu}
    - \frac{(\boldsymbol{\sigma \cdot \hat{\jmath}})(\boldsymbol{p_\nu \cdot \hat{\jmath}})}{E_\nu} \Bigg] \\
  + K'\frac{\boldsymbol{\sigma \cdot p_e}}{E_e+m_e} \Bigg[ \frac{1}{3}\frac{\boldsymbol{p_e \cdot p_\nu}}{E_e E_\nu}
    - \frac{(\boldsymbol{p_e \cdot \hat{\jmath}})(\boldsymbol{p_\nu \cdot \hat{\jmath}})}{E_e E_\nu} \Bigg] 
  + M \Bigg[ \frac{1}{3}\frac{\boldsymbol{\sigma \cdot p_e \times p_\nu}}{E_e E_\nu}
    - \frac{(\boldsymbol{\sigma \cdot \hat{\jmath}})(\boldsymbol{\hat{\jmath} \cdot p_e \times p_\nu })}{E_e E_\nu} \Bigg] \Bigg) \\
  + \boldsymbol{\sigma} \cdot \Bigg[ N\frac{\langle \boldsymbol{J} \rangle}{J}
    + Q\frac{\boldsymbol{p_e}}{E_e+m_e}\Bigg(\frac{\langle \boldsymbol{J} \rangle}{J}\boldsymbol{\cdot} \frac{\boldsymbol{p_e}}{E_e}\Bigg)
    + R\frac{\langle \boldsymbol{J} \rangle}{J}\boldsymbol{\times} \frac{\boldsymbol{p_e}}{E_e}
    + S\frac{\langle \boldsymbol{J} \rangle}{J} \frac{\boldsymbol{p_e\cdot p_\nu}}{E_e E_\nu} \\
    + T\frac{\boldsymbol{p_e}}{E_e}\frac{\langle \boldsymbol{J} \rangle}{J} \boldsymbol{\cdot} \frac{\boldsymbol{p_\nu}}{E_\nu}
    + U\frac{\boldsymbol{p_\nu}}{E_\nu}\frac{\langle \boldsymbol{J} \rangle}{J} \boldsymbol{\cdot} \frac{\boldsymbol{p_e}}{E_e}
    + W\frac{\boldsymbol{p_e}}{E_e+m_e}\frac{\langle \boldsymbol{J} \rangle}{J} \boldsymbol{\cdot} \frac{\boldsymbol{p_e \times p_\nu}}{E_e E_\nu}
    \Bigg]
  + V\frac{\langle \boldsymbol{J} \rangle}{J} \boldsymbol{\cdot} \frac{\boldsymbol{\sigma \times p_\nu}}{E_\nu}
  \Bigg\}
  \label{eq:jackson}
\end{multline}
%
where $F(\pm Z, E_e)$ is the Fermi function, $E$ is the energy of a given particle, $E^0$ is the endpoint
energy of the electron, $\boldsymbol{p}$ is the particle momentum, $\boldsymbol{J}$ is the spin of the
decaying nucleus (or nucleon), and $\sigma$ is the spin of the electron. All of the correlation coefficients
are functions of the coupling constants in the weak Lagrangian (see equation \ref{eq:leeyang}),
as is $\xi$. The correlation coefficients and $\xi$ are also functions of Fermi and Gamow-Teller
transition amplitudes. For the complete defitions see
\cite{jackson1957a,jackson1957b,ebel1957}.

Talk about the predictions Jackson makes given different conditions for the coefficients.



From \cite{jackson1957a}, we can write down the full expression (ignoring coulomb corrections)
for $A\xi$

\subsubsection{$V-A$ structure}

Discuss two component neutrino theory of Lee and Yang and the coupling of the fields to only
left handed fermions(?). Show how this selects maximal parity violation and talk about
experiments that confirm this ( i think in griffiths)



\subsection{Modern Weak Interaction in the Standard Model}
Talk about the existence of the weak interaction within the standard model and
the vertices and maybe write down the leptonic and hadronic current. Make it clear
that at low q squared, the Fermi's theory and Electroweak theory converge.

\subsubsection{Charged Weak Current}

\subsubsection{CKM Mixing Matrix}

\subsubsection{Neutral Current}

\section{What does this mean for the neutron?}

In the case of $\beta$-decay of polarized free neutrons and assuming the electron spin is undetectable,
equation \ref{eq:jackson} simplifies drastically,
%
\begin{multline}
  \frac{d\Gamma}{dE_e dE_\nu d\Omega_e d\Omega_\nu} = \frac{1}{2} \frac{F(\pm Z, E_e)}{\big( 2\pi \big)^5}
  p_e E_e \big( E^0 - E_e \big)^2 \\ \times \xi 
  \Bigg\{ 1 + a\frac{\boldsymbol{p_e \cdot p_\nu}}{E_e E_\nu} + b\frac{m_e}{E_e} 
  + \frac{\boldsymbol{\langle J \rangle}}{J} \Bigg[ A\frac{\boldsymbol{p_e}}{E_e}
    + B\frac{\boldsymbol{p_\nu}}{E_\nu} + D\frac{\boldsymbol{p_e \times p_\nu}}{E_e E_\nu}\Bigg]
  \Bigg\}.
  \label{eq:jacksonSimple}
\end{multline}
%

Switch to the more often used definitions of the coupling constants for consistency with modern literature
maybe...

\section{Ultracold Neutrons}

Talk about the typical energy spectra of neutrons from reactors and spallation sources. Show the
energy ranges and what we call each of the neutrons.

\subsection{Interactions}

\subsubsection{Fermi Potential}

\subsubsection{Gravity and Magnetic Fields}

\section{Summary}



