\documentclass[final]{ukthesis}
%you must include these 2 packages.
\usepackage{amsmath}

\usepackage[pdfauthor={Michael A.-P. Brown},
  pdftitle={Determination of the Neutron $\beta$-Decay Asymmetry
    Parameter $A_0$ Using Polarized Ultracold Neutrons},
            pdfsubject={The Subject},
            pdfkeywords={Some Keywords},
            pdfproducer={Latex with hyperref},
            pdfcreator={latex->dvips->ps2pdf},
            pdfpagemode=UseOutlines,
            bookmarksopen=true,
            bookmarksnumbered=true,
            hidelinks]{hyperref}

\usepackage{memhfixc}
\usepackage{float}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{csquotes}
\usepackage{mathtools}
\usepackage{gensymb}
\usepackage{rotating}
\usepackage{caption}

%\usepackage[small]{titlesec}
%\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{3}

%\changetocdepth{3}
%\maxsecnumdepth{subsection}
\setsecnumdepth{subsubsection}


\usepackage[
backend=bibtex,
%style=nature,
style=alphabetic,
%sorting=ynt
]{biblatex}
\addbibresource{references}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%author data
\author{Michael A.-P. Brown}
\title{Determination of the Neutron $\beta$-Decay Asymmetry
    Parameter $A_0$ Using Polarized Ultracold Neutrons}
\abstract{
  The UCNA Experiment at the Los Alamos Neutron Science Center (LANSCE) is the first measurement
  of the $\beta$-decay asymmetry parameter $A_0$ using polarized ultracold neutrons (UCN). $A_0$,
  which represents the parity-violating angular correlation between the direction of the initial
  neutron spin and the emitted decay electron's momentum, determines $\lambda=g_{A}/g_{V}$, the ratio
  of the weak axial-vector and vector coupling constants. A high-precision determination of
  $\lambda$ is important for weak interaction physics, and when combined with the neutron lifetime
  it permits an extraction of the CKM matrix element $V_{ud}$ solely from neutron decay. At LANSCE,
  UCN are produced in a pulsed, spallation driven solid deuterium source and then polarized via
  transport through a 7 T magnetic field. Their spins can then be flipped via transport through
  an Adiabatic Fast Passage spin flipper located in a low-field-gradient 1 T field region prior
  to transport to a decay storage volume situated within a 1 T solenoidal spectrometer. Electron
  detector packages located at each end of the spectrometer
  provide for the measurement of decay electrons. Previous
  UCNA results (based on data collected in 2010 and earlier) were limited by systematic
  uncertainties, in particular those from the UCN polarization, calibration of the electron
  energy, electron backscattering, and angular acceptance of events.
  This dissertation will present a background of Neutron
  Decay, an overview of the UCNA Experiment, followed by a detailed report on the entire analysis
  process for data acquired during run periods in 2011-2012 and 2012-2013.}

\advisor{Dr. Bradley Plaster}
\keywords{UCN, Neutrons}
\dgs{Dr. Chris Crawford}
%the title pages
\frontmatter
\maketitle


\begin{dedication}
  I dedicate this to my daughter, Scarlett Marie, for whom I am completing this thesis in a timely manner, and
  also, to those who I have lost, my brother Kenny, stepfather Bill, and stepmother Diana. 
  
\end{dedication}

\begin{acknowledgments}
  First and foremost, this work was made possible through the
  guidance provided by Dr. Brad Plaster. I thank you and appreciate not only the countless
  hours we spent talking about physics, but also the friendship that has developed. I also would
  like to thank Dr. Renee Fatemi, Dr. Susan Gardner, and Dr. Kevin Donohue for serving on
  my dissertation committee and seeing this process through. 

  I am very thankful to my entire family for constantly taking interest in everything I do.
  To my parents, Cindy Spurlin and John Wade Brown, I thank you from the bottom of
  my heart for pushing me to always be my best. I especially want to thank my loving
  wife Kirstie, as she not only celebrated the good times over the past seven years, but she
  endured the difficult times as well. You are my rock, and you are the reason I made it
  this far. Also to my wife's parents, Joe and Lisa Brangers, I would like to thank you for
  the immense amount of support you give me and Kirstie. We appreciate you more than you could know.
  Last but not least, I thank my best dog friend Piper for keeping me sane.

  I have been blessed with friends, old and new, who I want to thank for making life more enjoyable
  throughout this process.
  To all of my Crossfit friends in Frankfort and to my college golf teammates, the time
  we have spent together has been a necessary and welcomed distraction from my research. To my
  childhood friends, thank you for the love you show even when we are separated by thousands of miles
  at times. To all of the UCNA collaborators who I have had the privelege of working alongside,
  thank you for always being willing to help and for making research enjoyable.
  The list of friends would not be complete without giving a special thank you to Dr. Nima Nouri
  and Dr. Kevin Adkins. Nima, we sat together in the same lab for five years, and we made every effort
  to not mention physics to each other, which led to a friendship built for a lifetime.
  And Kevin, cheers to ten years of doing physics together, from
  undergrad through graduate school, through your wedding and mine, and finally to a daughter for each
  of us. Thank you for the time we spent learning physics together, but more importantly thank you for
  your friendship.
  
\end{acknowledgments}

\tableofcontents\clearpage
\listoffigures\clearpage
\listoftables\clearpage

%----------------------------------------------

\mainmatter
%\DoubleSpacing
\OnehalfSpacing

% Chapter 1
%\chapter{Introduction to the theory of neutron $\beta$-decay}
\include{1-Introduction/Introduction}
\copyrightnotice

% Chapter 2
%\chapter{UCNA Experiment}
\include{2-UCNAExperiment/UCNAExperiment}
\copyrightnotice

% Chapter 3
%\chapter{UCNA Analysis}
\include{3-UCNAAnalysis/UCNAAnalysis}
\copyrightnotice

% Chapter 4
%\chapter{UCNA Calibrations}
\include{4-UCNACalibrations/UCNACalibrations}
\copyrightnotice

% Chapter 5
%\chapter{UCNA Calibrations}
\include{5-UCNAResults/UCNAResults}
\copyrightnotice

% Appendix 1
%\include{Appendix1_magField/Append1}
%\copyrightnotice


%-----------------------------------------------
\backmatter

\printbibliography[title={References}]
%\bibliographystyle{alpha}
%\bibliography{references}

%\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}

%\setcounter{tocdepth}{0}
\chapter{Vita}

\section*{Personal Information}
\begin{tabular} {ll}
  Name: & Michael Anthony-Paul Brown \\
  Place of Birth: & Cincinnati, OH 
\end{tabular}

\section*{Educational Institutions}
\begin{tabular} {l}
  M.S. Physics    \\ University of Kentucky, Lexington, KY   \\May 2014 \\ \\
  B.S. Physics    \\ Morehead State University, Morehead, KY \\May 2011 \\ \\
  B.S. Mathematics\\ Morehead State University, Morehead, KY \\May 2011
\end{tabular}

\section*{Professional Positions}
\begin{tabular} {l}
  Graduate Research Assistant \\University of Kentucky, Lexington, KY \\
  Department of Physics and Astronomy\\
  January 2012 $-$ January 2018 \\
  \\
  Graduate Teaching Assistant \\University of Kentucky, Lexington, KY \\
  Department of Physics and Astronomy \\
  August 2011 $-$ December 2011 \\
  \\
  Undergraduate Research Assistant\\
  Research Experience for Undergraduates (REU)\\
  Duke University, Durham, NC \\
  Department of Physics \\
  May 2010 $-$ August 2010
 
\end{tabular}


\section*{Publications}
\begin{tabular} {l}
  Brown, M. A.-P., et al. "New result for the neutron $\beta$-asymmetry \\
  parameter $ A_0 $ from UCNA." Physical Review C 97 (2018): 035505. \\
  \\
  Hickerson, K. P., et al. "First direct constraints on Fierz interference \\
  in free-neutron β decay." Physical Review C 96.4 (2017): 042501.\\
  \\
  Broussard, L. J., et al. "Detection system for neutron β decay correlations\\
  in the UCNB and Nab experiments." Nuclear Instruments and Methods in Physics\\
  Research Section A: Accelerators, Spectrometers, Detectors and Associated\\
  Equipment 849 (2017): 83-93.\\
  \\
  Nouri, N., et al. "Frequency Shifts Induced by Field Gradients in Muon $g-2$\\
  Experiments." arXiv preprint arXiv:1607.04691 (2016).\\
  \\
  Nouri, N., et al. "A prototype vector magnetic field monitoring system for \\
  a neutron electric dipole moment experiment." Journal of Instrumentation\\
  10.12 (2015): P12003.\\
  \\
  MacMullin, S., et al. "Measurement of the elastic scattering cross section \\
  of neutrons from argon and neon." Physical Review C 87.5 (2013): 054613.
  
\end{tabular}

\end{document}
